---
title: "Intro to Agent-Based Modeling (ABM) through Modeling Mass Opinion Dynamics"
author: "Dale Frakes"
date: "9 July 2019"
output:
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About This Tutorial Session

### Description
This tutorial session will demonstrate building some basic agent-based models (ABM) of population
opinion dynamics in NetLogo. It will start by exploring various published opinion dynamics models
(e.g. Zaller-Deffuant model). It will then continue with specific NetLogo topics such as implementing
network models and extracting data from models for analysis.

### Who Should Attend?
This tutorial is aimed at two groups: 1) people who have little experience with ABM (particularly
NetLogo) and would like to develop their skills with an interesting social science problem, 2) people
who have some ABM experience and would like to explore a few ways of modeling opinion dynamics
using ABM.

## Acknowledgements

I would like to thank the following for making this tutorial possible:

* SBP-BRiMS and its organizers, particularly Dr. Kathleen Carley
* Dr. Wayne Wakeland, my PhD advisor at Portland State University
* Dr. William Burns, of Decision Research

## About the Presenter

Dale Frakes is a Ph.D. candidate in the Systems Science program at Portland State University, working
under Dr. Wayne Wakeland. He developed and teaches a course, “Modeling & Simulation with R &
Python” as well as teaching the program’s course in Agent Based Modeling. He is currently working
with two academic teams applying computer modeling to research on “Fake News” and
Intergenerational Obesity.

## Tutorial Materials

### NetLogo
This tutorial uses NetLogo, a popular, user-friendly, and open-source system for developing Agent Based Models.  It's freely available from Northwestern University:

<https://ccl.northwestern.edu/netlogo/>.

### Tutorial Files
The NetLogo model files and presentation materials are available from GitHub:

<https://github.com/dalefrakes/netlogo-tutorial>

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

